Social Feedback For Robotic Collaboration

### 2016-05-19 paper.tex
fixes

\begin{abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we describe a Partially Observable Markov Decision Process that incorporates the human's belief about the robot's intent. We then engineer a system that can respond in near-real time that is supplemented with a multithreaded interaction model that allows for more responsive human-robot interactions. Initial evaluation in simulation shows improvement in interaction length in a toy domain and improvement in accuracy in the full domain.
\end{abstract}

@@

POMDP approaches to dialog~\citep{young13} are quite common, but treat dialog
as a discrete, turn-taking interaction. The Dialog State Tracking
Challenge~\citep{williams2013dialog} a notable driving force for computer
dialog understanding, treats dialog in this turn-based way. Our model is also based off a turn-based interaction, but we provide a systems solution to allow our model to behave more incrementally.

@@

We represent human states $s_t$, robot states $\sigma_\tau$, and observations generated by the robot $\omega_\tau$ and by the human $o_{t}$. Observe that the structure of this model resembles two POMDPs combined together at their actions and observations. The lower POMDP is the POMDP from the human's perspective: the robot has some hidden states $\sigma_\tau$, which the human observes by means of $\omega_{t}$. The human takes actions $o_{t}$ to influence the robot's state $\sigma_t$. The upper POMDP models the interaction from the robot's perspective: the human's state $s_t$ is hidden from the robot, and the robot must infer it from observations $o_{t}$. When the robot takes action $\omega_{\tau-1}$, it affects the human's state $s_t$. Crucially, each agent treats the other agent's action as an observation that influences their belief about the other agent's hidden state. Thus, the human's actions affect the robot's belief about the human's state, which is what we call $b$ above. Importantly, the reverse is also true: the robot's actions affect the human's belief about what the robot's hidden state is. We will call the human's belief over the robot's hidden state $\beta$.

@@

\subsection{Incremental System Design}

\tikzstyle{block} = [rectangle, draw, fill=blue!20, text width=8em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, > = stealth, -latex]

\begin{figure*}
\begin{center}
\begin{tikzpicture}[auto]
	\node [block] (st) {State Tracker}; 
	\node [left = 2.5cm of st] (n) {};
	\node [block, right = 2.5cm of st] (ap1) {Asynchronous Planner}; 
	\node [block, above = 0.5cm of ap1] (ap2) {Asynchronous Planner}; 
	\node [block, below = 0.5cm of ap1] (ap3) {Asynchronous Planner};
	\node [block, right = 2.5cm of ap1] (aq) {Action Queue};
	\path [line] (st) -- node[above] {belief state} (ap1); 
	\path [line] (st) |- node[above right, pos=0.72] {belief state} (ap2); 
	\path [line] (st) |- node[above right, pos=0.72] {belief state} (ap3); 
	\path [line] (ap1) -- node[above] {action} (aq); 
	\path [line] (ap2) -| node[above left, pos=0.22] {acton} (aq); 
	\path [line] (ap3) -| node[above left, pos=0.22] {acton} (aq); 
	\path [line] (n) -- node[above]{observations} (st);
\end{tikzpicture}
\caption{An overview of multithreaded robot interaction framework. Each node is run on a separate thread. Edges are labeled with the type of data transmitted}
\label{fig:system}. 
\end{center}
\end{figure*}

Interactive systems that involve speech often make an assumption that the interaction can be split neatly into turns: first one speaker provides a complete utterance, and then the other. This is often not the case, and it is a subtle matter to determine when one turn is completed and the other agent can begin to speak. As a consequence, many systems involving dialogue, including earlier iterations of this project, do not ``hear'' utterances or gestures while the agent is speaking or acting. Any speech or gestures the human made while the robot was executing its action were dropped and never incorporated into the robot's belief about the state. An additional problem was that while the robot was planning its next action, it would also not incorporate any observations made. This was a significant effect, as it could take up to 10 seconds of planning for the robot to make its next move. As a consequence, most observations would be dropped unless we incorporated a system of turn-taking where we waited a set amount of time for the human to provide any speech and gesture input.

In order to create more fluid interactions, we employ a multithreaded solution that separates the state estimation, planning, and executions of actions. This allows our robot to simultaneously track the human's belief, plan its next move, and interact with the human. A diagram of the system is available in figure~\ref{fig:system}

\paragraph{State Tracker} The state tracker incorporates observations from the human at a very high rate, allowing the tracker to always have access to the most up to date state estimation. However, our domain description requires the robot to choose an action between each consecutive observation. We address this by feeding the model a \texttt{wait} action unless the planning thread has provided a different action. This requires minimal dependency between actions and observations, which our model avoids.

\paragraph{Asynchronous Planner} A separate thread runs the planning code. Planning can take several seconds, during which the robot is not only idle, but also deaf and blind. Running the planning code on a separate thread allows the robot to continue observing and interacting with the human while the robot plans its next move. In addition, we can use several planning threads at once, with separate policies to control the robot's face, arms, head angle, etc. In our work, we use one thread to plan for the POMDP domain described above, and another to animate the Baxter's face to show facial expression of increasing confusion with the entropy of the belief state.

\paragraph{Action Queue} The planning threads push their actions onto a queue which executes them one by one, allowing the planning threads to resume planning if the actions they produce take some time to execute. An additional advantage is that this allows the robot to be constantly acting, with minimal idle time.

>>>>

\begin{abstract}
Robotic collaboration requires not just communication from the human to the robot, but also from the robot to the human. We call this robot-to-human communication \emph{social feedback}. In order to flexibly and intelligently generate social feedback, we describe a partially Observable Markov Decision Process that incorporates the human's belief about the robot's intent. Doing so incentivizes the robot to communicate its current state in order to allow the human participant to make informed decisions about their next actions. Initial evaluation in simulation shows improvement in interaction length in a toy domain while maintaining near-perfect accuracy. 
\end{abstract}

@@

POMDP approaches to dialog~\citep{young13} are quite common, but treat dialog
as a discrete, turn-taking interaction. The Dialog State Tracking
Challenge~\citep{williams2013dialog} a notable driving force for computer
dialog understanding, treats dialog in this turn-based way. Our model is also based off a turn-based interaction, but is designed such that it would be suitable for a more incremental approach given the appropriate framework.

@@

WE represent human states $s_t$, robot states $\sigma_\tau$, and observations generated by the robot $\omega_\tau$ and by the human $o_{t}$. Observe that the structure of this model resembles two POMDPs combined together at their actions and observations. The lower POMDP is the POMDP from the human's perspective: the robot has some hidden states $\sigma_\tau$, which the human observes by means of $\omega_{t}$. The human takes actions $o_{t}$ to influence the robot's state $\sigma_t$. The upper POMDP models the interaction from the robot's perspective: the human's state $s_t$ is hidden from the robot, and the robot must infer it from observations $o_{t}$. When the robot takes action $\omega_{\tau-1}$, it affects the human's state $s_t$. Crucially, each agent treats the other agent's action as an observation that influences their belief about the other agent's hidden state. Thus, the human's actions affect the robot's belief about the human's state, which is what we call $b$ above. Importantly, the reverse is also true: the robot's actions affect the human's belief about what the robot's hidden state is. We will call the human's belief over the robot's hidden state $\beta$.

@@
